### 2023-04-10 output/group_0_crimes_1000m/tables/balance_table.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_0_crimes_1000m & 4,045.37 & 166.28 & 0.04 & -69.59 & 0.38 \\
 & pre_treatment_change_in_group_0_crimes_1000m & -25.13 & -2.31 & 0.02 & 0.42 & 0.66 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.47 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -282.14 & 0.85 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -836.74 & 0.34 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & -0.00 & 0.36 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & -396.20 & 0.37 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & no_cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.91 \\
 & non_payment & 0.77 & -0.08 & 0.00 & -0.01 & 0.26 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyD & 0.07 & -0.03 & 0.00 & -0.00 & 0.88 \\
 & isEntityD & 0.02 & -0.01 & 0.06 & -0.00 & 0.94 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & -0.01 & 0.23 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 0 Incidents, 2017 & 3,981.99 & 163.75 & 0.04 & -99.78 & 0.18 \\
 & $\Delta$ Group 0 Incidents, 2017-2019 & -490.95 & -20.32 & 0.20 & 12.30 & 0.43 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.28 \\
 & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & -398.45 & 0.79 \\
 & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & -0.01 & 0.17 \\
 & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & -573.69 & 0.16 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & Filing without cause & 0.05 & 0.00 & 0.95 & -0.00 & 0.87 \\
 & Filing for nonpayment & 0.77 & -0.08 & 0.00 & -0.02 & 0.08 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & Defendant has attorney & 0.07 & -0.03 & 0.00 & -0.00 & 0.80 \\
 & Defendant is entity & 0.02 & -0.01 & 0.06 & -0.00 & 0.90 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-10 output/group_0_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_1000m & 0.00 & 0.04 \\
 & pre_treatment_change_in_group_0_crimes_1000m & 0.00 & 0.02 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.02 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.11 & 0.00 \\
 & no_cause & 0.00 & 0.95 \\
 & non_payment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.01 & 0.00 \\
 & hasAttyP & 0.69 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.05 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 0 Incidents, 2017 & 0.00 & 0.04 \\
 & $\Delta$ Group 0 Incidents, 2017-2019 & 0.00 & 0.20 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
 & Job density, 2013 & 0.00 & 0.10 \\
 & Median household income, 2016 & 0.71 & 0.05 \\
 & Poverty rate, 2010 & 0.00 & 0.96 \\
 & Population density, 2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.06 & 0.00 \\
 & Filing without cause & 0.01 & 0.95 \\
 & Filing for nonpayment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.01 & 0.00 \\
 & Plaintiff has attorney & 0.33 & 0.00 \\
 & Defendant is entity & 0.00 & 0.06 \\
 & Plaintiff is entity & 0.22 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-10 output/group_1_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
 & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
 & no_cause & 0.67 & 0.95 \\
 & non_payment & 0.28 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
 & hasAttyP & 0.51 & 0.00 \\
 & isEntityD & 0.28 & 0.06 \\
 & isEntityP & 0.92 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.09 \\
 & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.38 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
 & Job density, 2013 & 0.00 & 0.10 \\
 & Median household income, 2016 & 0.00 & 0.05 \\
 & Poverty rate, 2010 & 0.00 & 0.96 \\
 & Population density, 2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.44 & 0.00 \\
 & Filing without cause & 0.11 & 0.95 \\
 & Filing for nonpayment & 0.10 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.00 & 0.00 \\
 & Plaintiff has attorney & 0.00 & 0.00 \\
 & Defendant is entity & 0.00 & 0.06 \\
 & Plaintiff is entity & 0.04 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-10 output/group_2_crimes_1000m/tables/balance_table.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 59.19 & 3.58 & 0.18 & 0.65 & 0.80 \\
 & pre_treatment_change_in_group_2_crimes_1000m & -0.67 & -0.05 & 0.50 & -0.01 & 0.93 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.70 & 0.94 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.73 & 0.49 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.67 & 0.52 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 2 Incidents, 2017 & 58.13 & 3.46 & 0.19 & 0.12 & 0.96 \\
 & $\Delta$ Group 2 Incidents, 2017-2019 & -10.95 & -0.05 & 0.92 & -0.03 & 0.96 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.93 \\
 & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 29.56 & 0.98 \\
 & Median household income, 2016 & 48,534.18 & 1,788.07 & 0.05 & 104.87 & 0.91 \\
 & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.90 \\
 & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 47.81 & 0.91 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.99 \\
 & Plaintiff is entity & 0.81 & -0.07 & 0.00 & 0.00 & 0.82 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-10 output/group_2_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.18 \\
 & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.50 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
 & no_cause & 0.16 & 0.95 \\
 & non_payment & 0.14 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.67 & 0.00 \\
 & hasAttyP & 0.13 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.53 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.19 \\
 & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.92 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
 & Job density, 2013 & 0.00 & 0.10 \\
 & Median household income, 2016 & 0.00 & 0.05 \\
 & Poverty rate, 2010 & 0.00 & 0.96 \\
 & Population density, 2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.96 & 0.00 \\
 & Filing without cause & 0.72 & 0.95 \\
 & Filing for nonpayment & 0.92 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.41 & 0.00 \\
 & Plaintiff has attorney & 0.44 & 0.00 \\
 & Defendant is entity & 0.00 & 0.06 \\
 & Plaintiff is entity & 0.04 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-10 output/group_3_crimes_1000m/tables/balance_table.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_3_crimes_1000m & 415.94 & 15.64 & 0.04 & 0.55 & 0.94 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.96 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 19.55 & 0.99 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 64.10 & 0.94 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.94 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 29.70 & 0.95 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & 0.00 & 0.89 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & 0.00 & 0.89 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & Total Group 3 Incidents, 2017 & 410.15 & 15.31 & 0.04 & -1.86 & 0.79 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.33 & 0.01 & 0.22 & -0.00 & 0.85 \\
 & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & -66.40 & 0.96 \\
 & Median household income, 2016 & 48,534.18 & 1,788.07 & 0.05 & -220.39 & 0.80 \\
 & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & -101.84 & 0.81 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has attorney & 0.88 & -0.04 & 0.00 & -0.00 & 0.65 \\
 & Plaintiff is entity & 0.81 & -0.07 & 0.00 & -0.00 & 0.65 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-10 output/group_3_crimes_1000m/tables/pre_treatment_covariate_tests.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_1000m & 0.00 & 0.04 \\
 & pre_treatment_change_in_group_3_crimes_1000m & 0.61 & 0.17 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
 & no_cause & 0.26 & 0.95 \\
 & non_payment & 0.95 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.99 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.15 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.04 \\
 & $\Delta$ Group 3 Incidents, 2017-2019 & 0.05 & 0.05 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.22 \\
 & Job density, 2013 & 0.00 & 0.10 \\
 & Median household income, 2016 & 0.00 & 0.05 \\
 & Poverty rate, 2010 & 0.37 & 0.96 \\
 & Population density, 2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.43 & 0.00 \\
 & Filing without cause & 0.30 & 0.95 \\
 & Filing for nonpayment & 0.92 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.95 & 0.00 \\
 & Plaintiff has attorney & 0.00 & 0.00 \\
 & Defendant is entity & 0.14 & 0.06 \\
 & Plaintiff is entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-10 output/summary_statistics/tables/summary_statistics.tex
Easy switching between monthly and weekly analysis

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{6}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & pre_treatment_change_in_group_0_crimes_100m & -0.30 & 0.00 & 2.38 & 6,060 \\
 & pre_treatment_change_in_group_1_crimes_100m & 0.02 & 0.00 & 0.66 & 6,060 \\
 & pre_treatment_change_in_group_2_crimes_100m & 0.03 & 0.00 & 0.68 & 6,060 \\
 & twenty_seventeen_group_0_crimes_100m & 2.32 & 2.00 & 2.83 & 6,060 \\
 & twenty_seventeen_group_1_crimes_100m & 0.17 & 0.00 & 0.47 & 6,060 \\
 & twenty_seventeen_group_2_crimes_100m & 0.19 & 0.00 & 0.47 & 6,060 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.31 & 0.24 & 0.22 & 6,060 \\
 & job_density_2013 & 14,806.08 & 2,425.15 & 40,595.37 & 6,060 \\
 & med_hhinc2016 & 47,188.87 & 41,146.00 & 24,703.65 & 6,060 \\
 & poor_share2010 & 0.28 & 0.25 & 0.14 & 6,060 \\
 & popdensity2010 & 22,704.52 & 20,644.44 & 13,091.45 & 6,060 \\
\cline{1-6}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.17 & 0.00 & 0.37 & 6,060 \\
 & no_cause & 0.05 & 0.00 & 0.22 & 6,060 \\
 & non_payment & 0.78 & 1.00 & 0.42 & 6,060 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.08 & 0.00 & 0.27 & 6,060 \\
 & hasAttyP & 0.88 & 1.00 & 0.32 & 6,060 \\
 & isEntityD & 0.02 & 0.00 & 0.14 & 6,060 \\
 & isEntityP & 0.81 & 1.00 & 0.39 & 6,060 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & case_duration & 58.17 & 19.00 & 88.96 & 5,500 \\
 & defaulted & 0.19 & 0.00 & 0.39 & 6,060 \\
 & dismissed & 0.27 & 0.00 & 0.44 & 6,060 \\
 & heard & 0.03 & 0.00 & 0.17 & 6,060 \\
 & judgment & 1,938.57 & 0.00 & 5,337.87 & 6,060 \\
 & mediated & 0.40 & 0.00 & 0.49 & 6,060 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & group_0_crimes_100m_1_years_relative_to_treatment & 1.46 & 1.00 & 3.05 & 3,039 \\
 & group_0_crimes_100m_2_years_relative_to_treatment & 1.48 & 1.00 & 2.31 & 2,830 \\
 & group_1_crimes_100m_1_years_relative_to_treatment & 0.14 & 0.00 & 0.45 & 3,039 \\
 & group_1_crimes_100m_2_years_relative_to_treatment & 0.10 & 0.00 & 0.36 & 2,830 \\
 & group_2_crimes_100m_1_years_relative_to_treatment & 0.20 & 0.00 & 0.55 & 3,039 \\
 & group_2_crimes_100m_2_years_relative_to_treatment & 0.22 & 0.00 & 0.63 & 2,830 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & $\Delta$ Group 0 Incidents, 2017-2019 & -532.85 & 465.54 & 6,060 \\
 & Total Group 0 Incidents, 2017 & 4,068.25 & 2,258.29 & 6,060 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.22 & 6,060 \\
 & Job density, 2013 & 14,806.08 & 40,595.37 & 6,060 \\
 & Median household income, 2016 & 47,188.87 & 24,703.65 & 6,060 \\
 & Poverty rate, 2010 & 0.28 & 0.14 & 6,060 \\
 & Population density, 2010 & 22,704.52 & 13,091.45 & 6,060 \\
\cline{1-5}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.17 & 0.37 & 6,060 \\
 & Filing without cause & 0.05 & 0.22 & 6,060 \\
 & Filing for nonpayment & 0.78 & 0.42 & 6,060 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.08 & 0.27 & 6,060 \\
 & Plaintiff has attorney & 0.88 & 0.32 & 6,060 \\
 & Defendant is entity & 0.02 & 0.14 & 6,060 \\
 & Plaintiff is entity & 0.81 & 0.39 & 6,060 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 58.17 & 88.96 & 5,500 \\
 & Judgment by default & 0.19 & 0.39 & 6,060 \\
 & Case dismissed & 0.27 & 0.44 & 6,060 \\
 & Case heard & 0.03 & 0.17 & 6,060 \\
 & Money judgment & 1,938.57 & 5,337.87 & 6,060 \\
 & Case mediated & 0.40 & 0.49 & 6,060 \\
\cline{1-5}
\bottomrule
\end{tabular}
